Evaluating Sound Similarity Metrics for Differentiable, Iterative Sound-Matching

### 2025-08-27 revised_main.tex
Updates from Overleaf

>>>>

A digital audio synthesizer is any software used for the creation and manipulation of audio. The possibilities afforded by these synthesizers is infinite, leading to their widespread adaption by artists and sound-designers~\cite{lyons1997understanding,russ1999sound,stranneby2004digital}. A typical synthesizer has a number of parameterizable functions which affect the output sound in various ways, and the manual approach involves modifying the parameters until a desired sound is reached.

The automation of the aforementioned approach is often referred to as "sound-matching", with reduction of tinkering time and creation of ``interesting" sounds as the main motivators \cite{krekovic2019insights,turian2020sorry,horner1993machine,salimi2020make,esling2019flow,engel2020ddsp,mitchell2007evolutionary,shier2020spiegelib,masuda2021soundmatch,masuda2023improving}. Sound-matching involves a target sound and a similarity metric (or loss function), and a heuristic to find parameters for a synthesizer that replicate \textit{all} or \textit{some} of the characteristics of a target sound as best as possible~\cite{horner1993machine,mitchell2007evolutionary,masuda2023improving}. Despite decades of research, major gaps of knowledge prevent sound-matching as practical approach for sound-designers. Here we highlight major issues in the field, leading us to
